\section{Computational Setup}

The model used to study the DNA nanopiston in this thesis, is largely based on the model
previously devised by Bayoumi et al. The main variation between the two models lays in
the different coarse-grained models, used to simulate the DNA strands. As discussed in
Chapter 2, the Bayoumi model uses a bead-spring approach to simulate DNA strands, where
we use the more sophisticated oxDNA model. This DNA model gives a better
representation of the dynamics of DNA strands, at the same time allowing for accurate
simulations of the thermodynamic transitions in the DNA nanopiston.

Our simulations are performed using the popular molecular dynamics simulator,
LAMMPS.\cite{PLIMPTON19951} Employing the LAMMPS implementation of oxDNA developed by
Henri et al.,
it becomes possible to study the interactions between oxDNA strands and externally
defined particles.\cite{Henrich18} The initial configurations of the simulations are
generated using the
Moltemplate package, a general purpose molecule builder for LAMMPS.\cite{JEWETT2021}

The molecular dynamics simulations performed in this thesis utilises a Langevin
thermostat, more precisely the Dot-C Langevin integrator, also implemented by Henri et
al. This is a LAMMPS implementation of the “Langevin C” integrator developed by
Davidchack et al., falling in the class of rigid-body Langevin-type
integrators.\cite{Davidchack2015}
This type of thermostat separates the stochastic and deterministic parts of a Langevin
thermostat to efficiently take into account the extra degrees of freedom in the system,
arising from the non-spherical shape of the oxDNA beads. As is common practice in MD
simulations, the diffusion coefficient of the oxDNA strand is chosen larger then the
value of physical DNA. This is done to speed up the simulations, while ensuring its
physical accuracy.

The model is used to more accurately study the conformational fluctuations of
the DNA rotaxanes and develop understanding of the entropic interactions between the DNA
and the nanopore. Next the thermodynamic transitions in the operation cycle of the piston
are simulated using a forward flux sampling algorithm. The FFS algorithm is implemented
as a Python script, performing the simulations by interfacing with the Python API of
LAMMPS.
