\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

I would like to start with thanking the members of the statistical biophysics group in
which I performed this thesis. During the numerous group meetings, even though they were
on-line, I was ever fascinated by your interesting research.

Foremost, I would like to thank Professor Enrico Carlon for the opportunity to
conduct this research under his guidance. Already during my Bachelor
thesis, you were able to spark my enthusiasm for this research field and this enthusiasm
has only grown during the past years.

Secondly, I am grateful for the guidance given by Stefanos Nomidis, who guided me
during my bachelor thesis and also at the start of this project. Furthermore, a big
thank-you to the other members of the research group, Aderik and Enrico S., for the
interesting discussions and the willingness with which they always were prepared to help
me with my questions. Not forgetting my fellow Master thesis students, Midas and Merijn,
which I would like to thank for the interesting interactions we had during the past year.

I would also like to thank my family for always being my support during my
studies. I think it is no overstatement to say that completing these past five years
would not have been possible without your help. Not at least due to the helpful advise
and laughs, during the proof readings of this thesis. Despite not having a lot of
intellectual capacity and input in this thesis, I want to especially thank Boris, the
family dog, for forcing me to take regular study brakes while working from home.
Apologies to the birds and squirrels in the forest who did not always appreciate our
passing by.

Last but not least, I would like to thank the friends I made during the past years in
Leuven. Despite the different expectations we had for our last year, we made some
unforgettable memories of which many are still to come.
