\addcontentsline{toc}{chapter}{Abstract}
\chapter*{Abstract}

Autonomous molecular machines are ubiquitous in the machinery of life, collectively
driving the molecular processes in our cells. Inspired by these biological machines,
scientists
develop synthetic devices performing specialised operations at the nanoscale. In this
thesis we study a specific molecular machine designed by Bayoumi et al.\cite{Bayoumi21},
which is composed of a DNA-neutravidin piston trapped inside a ClyA nanopore.

Using the free energy of DNA hybridisation this molecular machine is able to perform
autonomous and active transport of DNA cargo both following or opposing an
external bias force. During each operating cycle of the nanopiston a DNA cargo
is transported from the cis- to the trans-side of the membrane, in which the piston is
embedded.

Due to the length scale associated with molecular machines performing in depth
experimental studies has been proven to be challenging. During this thesis we aim
to shed light on the operating principles of the nanopiston by using molecular dynamics
simulations. Motivated by the computational cost of classical all-atom simulations a
coarse-grained model of the DNA nanopiston is designed.

Entropic interactions between the DNA piston and the nanopore are thought to
play an important role in facilitating the DNA transport. Studying these effects reveal
two distinct origins of entropic forces. Large double stranded DNA is kept predominantly
outside of the pore's constriction, by the entropic penalty of confinement.  Whereas, the
flexible single stranded DNA also
endouvours to maximize its available configurational space by opposing confinement.

Consecutively the  conformational fluctuations of
the nanopiston are studied.  These simulations clearly show the importance of the
entropic interactions promoting the operation cycle.  The entropic
penalty of confining the flexible single stranded DNA components of the piston in the
nanopore enable the continuation of the hybridisation reactions.

In an attempt to study a full piston cycle, the hybridisation reactions driving the
operation are simulated using our coarse-grained
model. Due to the inherent difficulty of simulating these reactions an advanced
sampling method called forward flux sampling is needed.
While performing these simulations the main limitation of our coarse-grained model was
encountered. The compliance of the biological nanopore is found to be essential in
facilitating the hybridisation pathways, but is not yet incorporated in our current
model.

\cleardoublepage


% \todo{make more consise en clearer.}
% Autonomous molecular machines are ubiquitous in the machinery of life, driving molecular
% processes in our cells. Inspired by these biological machines, scientists develop
% synthetic devices performing specialised operations at the nanoscale. In this
% thesis we study a specific molecular machine designed by Bayoumi et al.\cite{Bayoumi21},
% which is composed of a DNA-neutravidin piston trapped inside a ClyA nanopore.
%
% Using the free energy of DNA hybridisation, this molecular machine is able to perform
% autonomous and active transport of DNA cargo both following or against an
% external bias. During each operating cycle of the nanopiston a DNA cargo
% is transported from the cis- to the trans-side of the membrane in which the piston is
% embedded.
%
% Due to the length scale associated with molecular machines, studying the mechanisms
% driving the operation cycle is experimentally challenging. During this thesis we aim
% to shed light on the operating principles of the nanopiston by using molecular dynamics
% simulations. Motivated by the computational cost of classical all-atom simulations, a
% coarse-grained model of the DNA nanopiston is designed. In this work we use the popular
% OxDNA model to simulate the DNA strands, where the other components of the complex
% are modelled using Lennard-Jones beads.
%
% Entropic interactions between the DNA piston and the nanopore are thought to
% play an important role in facilitating the DNA transport. The contribution of
% these effects are studied in a variation of the original molecular machine, where the
% fraction of double and single stranded DNA is varied. In our simulations we
% observe that an equilibrium is found between competing entropic forces. The large double
% stranded DNA is kept outside of the pore's constriction, while the flexible single
% stranded DNA strives to maximize its available configurational space.
%
% Having explored the entropic effects related to the confinement of DNA strands in the
% nanopore, next the typical conformations of the stable states in the operating cycle
% are simulated. Here the importance of the entropic interactions promoting the
% hybridisation reactions clearly come to light. The entropic penalty of confining the
% flexible single stranded DNA components of the piston in the nanopore enables the
% continuation of the operation cycle.
%
% \newpage
%
% In an attempt to gain an overall understanding of the transition pathways driving the
% molecular device, the hybridisation reactions are simulated using our coarse-grained
% model. Due to the inherent difficulty of simulating DNA hybridisation an advanced
% sampling method called forward flux sampling is needed to study these phenomena.
% While performing these simulations the limits of our coarse-grained model are
% encountered. The compliance of the biological nanopore is found to be essential in
% facilitating the hybridisation pathways, but is not incorporated in our current model.
